---
title: "Legislator's Demographic Data"
author: ""
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Legislator's Demographic Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
assign("has_internet_via_proxy", TRUE, environment(curl::has_internet))
```

## Using `get_legislators()` as an Example to Fetch Legislator Data

<div class="text-justify">

The get_legislators() function provides a straightforward way to access Taiwan's legislator data from the official parliamentary database. Here's a step-by-step demonstration:


</div>

```{r}
library(legisTaiwan)
```

<div class="text-justify">

First, we load the legisTaiwan package which contains tools for accessing Taiwan's legislative data.
</div>

```{r}
info <- get_legislators(verbose = FALSE)
```

<div class="text-justify">
Here, we call get_legislators() and store the results in info. The verbose = FALSE parameter suppresses the progress bar during data fetching. This makes the function run quietly without displaying download progress.
</div>

```{r}
info$data
```

<div class="text-justify">

This command displays the retrieved data which includes comprehensive information about legislators. The returned data frame contains various fields about each legislator, such as:

- Personal information (name, gender, birth date)
- Electoral district details
- Party affiliation
- Committee and more!

Each row represents a unique legislator, making it easy to analyze or extract specific information about Taiwan's parliamentary representatives.

</div>

