---
title: "The Records of the Bills"
author: ""
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The Records of the Bills}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include=FALSE}
assign("has_internet_via_proxy", TRUE, environment(curl::has_internet))
```


## An Example of the Records of the Bills

<div class="text-justify">

First, we'll import legisTaiwan, and then we'll retrieve data from January 20th of the Republic of China year 106 to March 10th of the Republic of China year 111.

</div>


```{r}
library(legisTaiwan)
```


```{r}
billdata <- get_bills(start_date = 1030120,end_date = 1110310, verbose = TRUE)
```

The get_bills function returns a list that contains query_time, retrieved_number, meeting_unit, start_date_ad (A.D) , end_date_ad (A.D), start_date, end_date, url, variable_names, manual_info, and data.
```{r}
billdata$data
```


```{r}
full_term <- get_bills_2(term = 11)
full_term
```

<!-- ```{r} -->
<!-- # 安裝套件 -->
<!-- install.packages("pdftools") -->
<!-- library(pdftools) -->

<!-- # 讀取 PDF -->
<!-- pdf_text <- pdf_text("https://ppg.ly.gov.tw/ppg/download/agenda1/02/pdf/11/01/02/LCEWA01_110102_00017.pdf") -->


<!-- # 文本清理 -->
<!-- library(stringr) -->
<!-- library(dplyr) -->

<!-- clean_text <- pdf_text %>% -->
<!--   str_replace_all("\n", " ") %>%  # 移除換行 -->
<!--   str_replace_all("\\s+", " ") %>%  # 移除多餘空白 -->
<!--   str_trim()  # 移除前後空白 -->

<!-- # 斷詞（如果需要） -->
<!-- library(jiebaR) -->
<!-- cutter <- worker() -->
<!-- words <- segment(clean_text, cutter) -->

<!-- library(httr) -->
<!-- library(pdftools) -->

<!-- # 下載 PDF -->
<!-- response <- GET(url) -->
<!-- writeBin(content(response, "raw"), temp_file) -->
<!-- pdf_text <- pdf_text(temp_file) -->
<!-- # 處理編碼問題（如果有需要） -->
<!-- pdf_text <- iconv(pdf_text, "UTF-8", "UTF-8") -->

<!-- # 如果要分頁處理，可以用以下方式： -->
<!-- for(i in seq_along(pdf_text)) { -->
<!--   cat("=== 第", i, "頁 ===\n") -->
<!--   cat(pdf_text[i]) -->
<!-- } -->
<!-- ``` -->

