---
title: "Quick Start"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Get Started with Using [`remotes`](https://github.com/r-lib/remotes):

<div style="text-align: justify">

**`legisTaiwan`** is an R package for accessing [Taiwan Legislative Yuan API](https://data.ly.gov.tw/index.action). The goal of `legisTaiwan` is to make it quickly and instantly download Taiwan's legislative data, digitized textual 
and video records for a research project and analyze public policies. 

</div>


```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("davidycliao/legisTaiwan", force = TRUE)
```

```{r}
library(legisTaiwan)
```


```{r include=FALSE}
assign("has_internet_via_proxy", TRUE, environment(curl::has_internet))
```



## Taiwan Legislative Yuan API (v2)

<div style="text-align: justify">

The Legislative Yuan API is transitioning from `https://ly.govapi.tw` to `https://v2.ly.govapi.tw`. 

While we are maintaining support for functions that use the legacy API, please note that the old API endpoint will eventually be deprecated. We recommend users to gradually transition to the newer API versions as they become available.

**Current Status:**

- Legacy API (`ly.govapi.tw`) - Still functional but will not receive updates
- New API (`v2.ly.govapi.tw`) - Current active development and maintenance

</div>

###  Statistical Information

- [`get_tly_stat()`](): Fetch and Parse Legislative Yuan Statistics


### Legislators 

- [`get_ly_legislator_detail()`](): Retrieve Complete Historical Records of Legislators
- [`get_ly_legislators_by_term()`](): Get Legislators by Legislative Term
- [`get_ly_legislator_cosign_bills()`](): Retrieve Legislator's Co-sponsored Bills
- [`get_ly_legislator_bills()`](): Get Bills Proposed by Legislator

### Bill 

- [`get_ly_bills()`](): Fetch and Parse Legislative Yuan Bills

### Committees 

- [`get_ly_committee_meets()`](): Fetch Legislative Yuan Committee Meetings

- [`get_ly_committees_type()`](): Fetch and Parse Legislative Yuan Committee Details, Jurisdiction and Codes

### Interpellation

- [`get_ly_interpellations()`](): Get Legislative Yuan Interpellation Records

###  IVOD

- [`get_ly_ivod()`](): Get Legislative Yuan IVOD Records

<br> 

## Taiwan Legislative Yuan API (v1)

We will provide comprehensive guides and documentation to help you migrate to the new API endpoints.

- [`get_parlquestions()`](https://davidycliao.github.io/legisTaiwan/reference/get_parlquestions.html): parliamentary questions asked by the legislators 提供議事日程本院委員之質詢事項資訊 (自第8屆)

- [`get_meetings()`](https://davidycliao.github.io/legisTaiwan/reference/get_bills.html): spoken meeting records 委員發言

- [`get_caucus_meetings()`](https://davidycliao.github.io/legisTaiwan/reference/get_caucus_meetings.html): the meeting records of cross-caucus session 提供公報之黨團協商資訊 (自第8屆)

- [`get_executive_response()`](https://davidycliao.github.io/legisTaiwan/reference/get_executive_response.html): questions answered by the executives提供公報質詢事項行政院答復資訊 (自第8屆)

- [`get_public_debates()`](https://davidycliao.github.io/legisTaiwan/reference/get_public_debates.html): public debates 提供公報之國是論壇資訊，並包含書面意見自 (自第8屆)

- [`get_speech_video()`](https://davidycliao.github.io/legisTaiwan/reference/get_speech_video.html): full video information of meetings and committees 提供立法院院會及委員會之委員發言片段相關影片資訊 (自第9屆)

- [`get_committee_record()`](https://davidycliao.github.io/legisTaiwan/reference/get_committee_record.html): the records of reviewed items in the committees 提供委員會會議審查之議案項目 (自第8屆)

- [`get_bills()`](https://davidycliao.github.io/legisTaiwan/reference/get_bills.html): the records of the bills 法律提案 (能取得最早日不詳，待檢查)

- [`get_bills_2()`](https://davidycliao.github.io/legisTaiwan/reference/get_bills_2.html): the records of legislators and the government bill proposals 提供委員及政府之議案提案資訊 (自第8屆)         

- [`passed_legislation()`](https://data.ly.gov.tw/getds.action?id=48): legislation and information passed on the third reading 提供公報院會紀錄之三讀通過議案資訊。(自第8屆第1會期起) **coming soon**

- [`get_variable_info()`](https://davidycliao.github.io/legisTaiwan/reference/get_variable_info.html): the API’s endpoint user manuals 使用說明文件

- [`review_session_info()`](https://davidycliao.github.io/legisTaiwan/reference/review_session_info.html): the session period and year in formatted in Minguo (ROC) calendar. 屆期年對照表


- [`get_legislators()`](https://davidycliao.github.io/legisTaiwan/reference/get_legislators.html): legislator demographics 提供委員基本資料

<br>

## How to Contribute

<div style="text-align: justify">
Contributions in the form of comments, code suggestions, and tutorial examples are very welcome. Please note that the `LeigsTaiwan` is released with the [Contributor Code of Conduct](https://github.com/davidycliao/legisTaiwan/blob/master/CONDUCT.md). By contributing to this project, you agree to abide by its terms. 

</div>

<br> 
