---
title: "Quick Start"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Get Started with Using [`remotes`](https://github.com/r-lib/remotes):


<div style="text-align: justify">

**`legisTaiwan`** is an R package for accessing [Taiwan Legislative Yuan API](https://data.ly.gov.tw/index.action). The goal of `legisTaiwan` is to make it quickly and instantly download Taiwan's legislative data, digitized textual 
and video records for a research project and analyze public policies. Its initial development was part of David Yen-Chieh Liao' Dissertation project **[Electoral Reform, Distributive Politics, and Parties in the Taiwanese Congress](https://raw.githack.com/davidycliao/phd-thesis/main/Yen_Chieh_Liao_PhD_Dissertation_Jan_2023.pdf)** supported by Taiwanese Overseas Pioneers Grant (TOP GRANT), the National Science and Technology Council (NSTC) of Taiwan. The package is, therefore, of great benefit to researchers, students, and policy analysts interested in Taiwan legislative politics (and Taiwan politics in general) with fewer financial resources. In addition, the annotation of digitized text and labelled topics of video records may be of interest to researchers and students who want to build an algorithm for computational research in social science as well as enhance transparency, accountability and democracy towards our country.

</div>


```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("davidycliao/legisTaiwan", force = TRUE)
```

```{r}
library(legisTaiwan)
```

<br> 

-----

## The Overview of the API Access  

<div style="text-align: justify">

| `legisTaiwan`                                                                                                 | Since (AD/ROC)  | Taiwan Legislative Yuan API                                                                                                                                                 |
|---------------------------------------------------------------------------------------------------------------|-----------------|-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| [`get_meetings()`](https://davidycliao.github.io/legisTaiwan/reference/get_bills.html)                        | 7th (2011/100)+ | [**spoken meeting records 委員發言 (能取得最早日不詳，待檢查)**](https://davidycliao.github.io/legisTaiwan/reference/get_bills.html)                                         |
| [`get_caucus_meetings()`](https://davidycliao.github.io/legisTaiwan/reference/get_caucus_meetings.html)       | 8th (2011/100)  | [**the meeting records of cross-caucus session 提供公報之黨團協商資訊 (自第8屆)**](https://data.ly.gov.tw/getds.action?id=8)                                                |
| [`get_bills()`](https://davidycliao.github.io/legisTaiwan/reference/get_bills.html)                           | 7th (2011/100)+ | [**the records of the bills 法律提案 (能取得最早日不詳，待檢查)**](https://davidycliao.github.io/legisTaiwan/reference/get_bills.html)                                       |
| [`get_bills_2()`](https://davidycliao.github.io/legisTaiwan/reference/get_bills_2.html)                       | 8th (2014/100)  | [**the records of legislators and the government bill proposals 提供委員及政府之議案提案資訊 (自第8屆)**](https://data.ly.gov.tw/getds.action?id=1)                        |
| [`get_legislators()`](https://davidycliao.github.io/legisTaiwan/reference/get_legislators.html)               | 2th (1992/81)   | [**legislator demographics 提供委員基本資料**](https://davidycliao.github.io/legisTaiwan/reference/get_legislators.html)                                                  |
| [`get_parlquestions()`](https://davidycliao.github.io/legisTaiwan/reference/get_parlquestions.html)           | 8th (2014/104)  | [**questions asked by the legislators 提供議事日程本院委員之質詢事項資訊 (自第8屆)**](https://davidycliao.github.io/legisTaiwan/reference/get_parlquestions.html)             |
| [`get_executive_response()`](https://davidycliao.github.io/legisTaiwan/reference/get_executive_response.html) | 8th (2014/104)  | [**questions answered by the executives提供公報質詢事項行政院答復資訊 (自第8屆)**](https://davidycliao.github.io/legisTaiwan/reference/get_executive_response.html) |
| [`get_public_debates()`](https://davidycliao.github.io/legisTaiwan/reference/get_public_debates.html)         | 8th (2014/104)  | [**public debates 提供公報之國是論壇資訊，並包含書面意見自 (自第8屆)**](https://davidycliao.github.io/legisTaiwan/reference/get_public_debates.html)                           |
| [`get_speech_video()`](https://davidycliao.github.io/legisTaiwan/reference/get_speech_video.html)             | 8th (2014/104)  | [**full video information of meetings and committees 提供立法院院會及委員會之委員發言片段相關影片資訊 (自第9屆)**](https://data.ly.gov.tw/getds.action?id=148)               |
| [`get_committee_record()`](https://davidycliao.github.io/legisTaiwan/reference/get_speech_video.html)         | 8th (2014/104)  | [**the records of reviewed items in the committees 提供委員會會議審查之議案項目 (自第8屆)**](https://davidycliao.github.io/legisTaiwan/reference/get_speech_video.html)     |
| [`get_variable_info()`](https://davidycliao.github.io/legisTaiwan/reference/get_variable_info.html)           | 8th (2014/104)  | [**the API’s endpoint user manuals 使用說明文件**](https://davidycliao.github.io/legisTaiwan/reference/get_variable_info.html)                                       | 


[+ **Further Check Required**: the user manual seems to be inconsistent with actual data. Please check them out in the discussion 資料似乎不一致，待確認。](https://github.com/davidycliao/legisTaiwan/discussions)

</div>

<br> 

-----

## Tutorials

+ [取得歷屆委員資料為例 (李宜展 東海大學政治系)](https://davidycliao.github.io/legisTaiwan/articles/get_legislators.html)

<br> 

-----

## How to Contribute

Contributions in the form of comments, code suggestions, functions, and tutorial examples are very welcome:

- Fork the source code, modify, and issue a pull request through the project GitHub page are welcome. Please read the [Contributor Code of Conduct]([![codecov](https://codecov.io/gh/davidycliao/asmcjr/branch/master/graph/badge.svg?token=OJKOF5SX9X)](https://codecov.io/gh/davidycliao/asmcjr)).

- Regarding issues, bug reports, or wish lists, please [file a GitHub issue](https://github.com/davidycliao/legisTaiwan/issues).

- Contact the maintainer by email: _*davidycliao[at]cas.au.dk*_.
